\subsubsection{Global Small Business Usage Estimate}\label{sec:branches-small-bus-est}
The average annual electricity usage of a small business in four countries in four different regions is used to determine a global small business electricity usage estimate.
These four countries are the US, the UK, Mexico, and China.

The global estimated average annual electricity usage of a small business is calculated as follows:

\begin{align}\label{eqn:banks-e-total}
&E_\textrm{Bus} = \dfrac{ \sum \limits_{i=1} ^ {N_\textrm{Reg} } E_{\textrm{Bus,}i } }{ N_\textrm{Reg} }
\end{align}

Where,

\begin{align*}
&E_\textrm{Bus}  \textrm{ \ \   = Estimated average annual electricity usage of a small business, $\kwhyr$}  \\
&E_{\textrm{Bus,}i} \textrm{ \  = Small business electricity usage for the $i^{th}$ region in } \\ 
&\textrm{ \ \qquad \qquad summation, $\kwhyr$} \\ 
&N_\textrm{Reg} \textrm{ \ \ \  = Number of considered regions, 4}
\end{align*}

Both the US and the UK have small business electricity usage data readily available, but it is difficult to locate data regarding a small business's electricity usage in many other geographical locations, including Mexico and China.
Residential data, however, is available for all considered regions and is used in conjunction with the small business electricity usage data from the known regions in an attempt to make a fair estimate.

A ratio of a small business's annual electricity usage and a residential annual electricity usage for the countries with known data (the US and UK) is calculated as follows:

\begin{align}\label{eqn:banks-ratio-bus-reg}
  R_{\mlsub{Bus,} {Reg} } = \frac{ E_{\mlsub{Bus,} {Reg} } }{ E_{\mlsub{Res,} {Reg} } }
\end{align}

Where,


\begin{align*}
&R_{ \mlsub{Bus,} {Reg} } \textrm{  = Regional small business to residential electricity usage ratio } \\
&E_{\mlsub{Bus,} {Reg} } \textrm{   = Annual small business electricity usage for a specific region, $\kwhyr$} \\ 
&E_ { \mlsub{Res,} {Reg} } \textrm{ = Annual residential electricity usage for a specific region, $\kwhyr$}
\end{align*}

In 2019, the EIA reported that the monthly average electricity usage of a small business operating in the United States is 6,066 kWh/mo, or 72,792 kWh/yr \cite{us-business}.
Another report by the EIA last updated in 2019, reported that the annual average electricity usage of a residence in 2015 was 11,000 kWh/yr \cite{us-residential}.

Eq. \eqref{eqn:banks-ratio-bus-reg} for the US is solved as follows:

\begin{align}\label{eqn:banks-ratio-bus-us}
  R_\textrm{Bus, US} &= \frac{72,792 \ \kwhyr} {11,000 \ \kwhyr} \\
                     &= 6.62 \nonumber
\end{align}

In the UK, a small business uses 25,000 \cite{uk-business}.
The average UK household consumes about 10 kWh/day, for a total of 3,650 kWh/yr \cite{uk-residential}.

Eq. \eqref{eqn:banks-ratio-bus-reg} for the UK is solved as follows:

\begin{align}\label{eqn:banks-ratio-bus-uk}
  R_\textrm{Bus, UK} &= \frac{25,000 \ \kwhyr} {3,650 \ \kwhyr} \\
                     &= 6.85 \nonumber
\end{align}

The final ratio used is an average of the two ratios in Eq. \eqref{eqn:banks-ratio-bus-us} and \eqref{eqn:banks-ratio-bus-uk} and is defined as follows:

\begin{align}\label{eqn:banks-bus-ratio}
  R_\textrm{Bus} = \dfrac{ \sum\limits_{i=1}^{N_{\mlsub{Known} {Reg} } } R_{\mlsub{Bus,} {Known Reg$_i$} } } { N_{\mlsub{Known} {Reg} } }
\end{align}

Where,

\begin{align*}
&R_\textrm{Bus} \textrm{ \ \ \qquad \ \ = Average ratio of the small business to residential electricity} \\
&\textrm{\ \qquad \qquad \quad \ \ \ \ usage ratios for the known regions} \\
&i \textrm{\ \quad \qquad \qquad = Summation start index} \\
&N_{\mlsub{Known} {Reg} } \textrm{ \quad \ = Number of known regions} \\
&R_{\mlsub{Bus} {Known Reg$_i$} } \textrm{\ = Ratio $i_{th}$ region with known annual small business electricity} \\
&\textrm{\ \qquad \qquad \quad \ \ \ \ usage ratios for the known regions} \\
\end{align*}

The results of Eq. \eqref{eqn:banks-ratio-bus-us} and \eqref{eqn:banks-ratio-bus-uk} are similar in number, lending credence to the accuracy of this method.

Using the results of Eq. \eqref{eqn:banks-ratio-bus-us} and \eqref{eqn:banks-ratio-bus-uk}, Eq. \eqref{eqn:banks-bus-ratio} is solved as follows:

\begin{align}\label{eqn:banks-bus-ratio-res}
  R_\textrm{Bus} &= \frac{ 6.62 + 6.85 } { 2 } \\
                 &= 6.73 \nonumber
\end{align}

Using the resulting ratio defined in Eq.\eqref{eqn:banks-bus-ratio-res}, the annual electricity usage of a small business in regions with residential data only is defined as follows:

\begin{align}\label{eqn:banks-bus-unknown-region}
&E_{\mlsub{Bus,} {Unknown Reg} } = R_\textrm{Bus} \times E_{\mlsub{Res,} {Reg} }
\end{align}

Where,

\begin{align*}
&E_{\mlsub{Bus,} {Unknown Reg} } = \textrm{ Estimated total annual small business electricity usage for } \\
&\textrm{\ \qquad \qquad \quad \quad \ \ \ \ region with no data, $\kwhyr$} \\
&R_\textrm{Bus} \textrm{ \ \ \qquad \ \ = Ratio of the average small business to residential electricity usage} \\
&\textrm{\ \qquad \qquad \quad \quad \ \ \ \ ratios for the known regions, 6.73} \\
&E_ { \mlsub{Res,} {Reg} } \textrm{ \quad \qquad \ = Annual residential electricity usage for a specific region, $\kwhyr$}
\end{align*}

In 2018, the Department of Architecture at the Universidad de las Americas Puebla reported that the daily average electricity usage of a household in Mexico consumes 4.76 kWh/day, or 1,737 kWh/yr \cite{residential-mexico}.

Eq. \eqref{eqn:banks-bus-unknown-region} for Mexico is solved as follows:

\begin{align}\label{eqn:banks-bus-mexico}
  E_{\mlsub{Bus,} {Mexico} } &= R_\textrm{Bus} \times E_{\mlsub{Res,} {Mexico} } \\
                             &= 6.73 \times 1,737 \ \kwhyr \nonumber \\
                             &= 11,699 \ \kwhyr \nonumber
\end{align}

In 2016, the American Council for an Energy-Efficient Economy estimates that in rural China the average residence uses 1,371 kWh/yr, and residences in more urban areas use 1,888 kWh/yr \cite{residential-china}.
An average of these two numbers is used for the small business electricity usage of China, which is found to be 1,630 kWh/yr.

Eq. \eqref{eqn:banks-bus-unknown-region} for China is solved as follows:

\begin{align}\label{eqn:banks-bus-china}
  E_{\mlsub{Bus,} {China} } &= R_\textrm{Bus} \times E_{\mlsub{Res,} {China} } \\
                            &= 6.73 \times 1,630 \ \kwhyr \nonumber \\
                            &= 10,972 \ \kwhyr \nonumber
\end{align}


Using the known annual small business electricity usage for the U.S. and the U.K., as well as the results of Eq. \eqref{eqn:banks-bus-mexico} and \eqref{eqn:banks-bus-china}, for Mexico and China, respectively, Eq. \eqref{eqn:banks-e-total} is solved as follows:

\begin{align}\label{eqn:banks-e-total-res}
  E_\textrm{Bus} &= \dfrac{ \sum \limits_{i=1} ^ {N_\textrm{Reg} } E_{\textrm{Bus,}i } }{ N_\textrm{Reg} }
                 &= \frac{ 72,792 \ \kwhyr + 25,000 \ \kwhyr + 11,699 \ \kwhyr + 10,972 \ \kwhyr } { 4 } \\
                 &= 30,116 \ \kwhyr \nonumber
\end{align}
