\subsection{Bitcoin Node Contribution}\label{sec:btc-nodes}
\subsubsection{Assumptions}
\begin{enumerate}
  \item The operating hours of a Bitcoin node is 24 hours per day, 7 days per week, 52 weeks per year, for a total of 8,760 hours per year.
  \item The number of nodes on the Bitcoin network vary as participants come on and off line for a variety of reasons.
    The number of nodes used in this report is from a network snapshot taken on April 23rd, 2021.
  \item The demand of a single node on the network is estimated to be the average of a standard laptop, a Raspberry Pi 4, and a 4-core CPU and disk space.
    This is a conservative estimate considering a Bitcoin node may not consume all of the hardware's resources.
\end{enumerate}

\subsubsection{Methodology}
The estimated total annual electricity usage required to operate the nodes on the Bitcoin network is calculated as follows:

\begin{align}\label{eqn:btc-node-e}
E_\textrm{Nodes} = N_\textrm{Nodes} \times D_\textrm{Node} \times H_\textrm{yr} \times C
\end{align}

\noindent
Where,

\begin{align*}
&E_\textrm{Nodes} \textrm{            = Estimated total annual electricity usage of Bitcoin nodes, $\xwhyr{T}$} \\
&N_\textrm{Nodes} \textrm{\           = Number of nodes on the Bitcoin network, 11,740 nodes \cite{btc-moody-dash}} \\
&D_\textrm{Node}  \textrm{\ \         = Estimated average demand of Bitcoin node hardware, 0.52 kW} \\
&H_\textrm{yr}    \textrm{\quad \ \   = Operating hours of a Bitcoin node, 8,760 $\hyr$} \\
&C                \textrm{\qquad \ \  = Conversion factor, $\convtk$}
\end{align*}

The operating hours of a Bitcoin node is 24 hours per day, 7 days per week, 52 weeks per year, for a total of 8,760 hours per year.
The number of nodes on the Bitcoin network on April 23rd, 2021 are 11,740 \cite{btc-moody-dash}.
The system requirements to run a full node are minimal.
Currently, most systems with around 500 GB of storage and a 4-core CPU are capable of running a node.
Because of this, Bitcoin nodes are run on various types of hardware, including laptops, simple servers, and Raspberry Pi's.
An average laptop consumes 60W, a Raspberry Pi 4 consumes a maximum of 15.3 W, and a typical 4-core CPU server and disk space consumes 81W \cite{laptop-demand, rpi-demand, intel-4-core, ssd-demand}.
The demand of hardware running a Bitcoin node is estimated to be the average of these three pieces of hardware.
This is a conservative estimate considering a Bitcoin node may not consume all of the hardware's resources.

Therefore, the estimated average demand required to operate a Bitcoin node is calculated as follows:

\begin{align}\label{eqn:btc-node-demand}
  D_\textrm{Node} = \frac{D_\textrm{4-core} + D_\textrm{laptop} + D_\textrm{RPi}} {N_\textrm{HW}} \times C
\end{align}

\noindent
Where,

\begin{align*}
&D_\textrm{Node}    \textrm{ \ \            = Estimated average demand of hardware running a Bitcoin node, kW} \\
&D_\textrm{4-core}  \textrm{ \              = Demand of a server with a 4-core CPU and disk space, 81W \cite{intel-4-core, ssd-demand}} \\
&D_\textrm{Laptop}  \textrm{                = Demand of a typical laptop, 60W \cite{laptop-demand}} \\
&D_\textrm{RPi}     \textrm{ \quad \        = Demand of a Raspberry Pi 4, 15.3W \cite{rpi-demand}} \\
&N_\textrm{HW}      \textrm{ \quad \        = Number of hardware configurations considered, 3} \\
&C                  \textrm{\qquad \quad \  = Conversion factor, $\convkw$}
\end{align*}

Eq. \eqref{eqn:btc-node-demand} is solved as follows:

\begin{align}\label{eqn:btc-node-demand-res}
D_\textrm{Node} &= \tfrac{81 \textrm{ W} + 60 \textrm{ W} + 15.3 \textrm{ W}} { 3 }  \times \convkw \nonumber \\
&= 0.52  \textrm{ kW}
\end{align}

Using the known number of nodes and the resulting estimated demand of a single node from Eq. \eqref{eqn:btc-node-demand-res}, Eq. \eqref{eqn:btc-node-e} is solved as follows:

\begin{align}\label{eqn:btc-node-e-res}
  E_\textrm{Nodes} &= N_\textrm{Nodes} \times D_\textrm{Node} \times H_\textrm{yr} \times C \nonumber \\
                   &= 11,740 \times 0.52 \kwhyr \times 8,760 \hyr \times \convtk \nonumber \\
                   &=  5,358,089.04 \kwhyr \times \convtk \nonumber \\
                   &=  0.0054 \xwhyr{T}
\end{align}

Therefore, the estimated total annual electricity usage of all Bitcoin nodes is 0.0054 $\xwhyr{T}$.
